Differentially Private Bayesian Inference

### 2018-04-09 main.tex
update dilation property

Since the sensitivity is always greater than 0, but the utility function and $\lambda$ can be positive or negative. That's what we need to discuss.

\begin{itemize}
	\item $\lambda > 0$
	\begin{itemize}
		\item $u(r) > 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.

		\item $u(r) < 0$

		% This need to be discuss further.
		% We can have:
		% \begin{equation*}
		% \lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
		% \end{equation*}

	\end{itemize}
	\item $\lambda < 0$
	\begin{itemize}
		\item $u(r) > 0$

		% This need to be discuss further.
		% We can have:
		% \begin{equation*}
		% \lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
		% \end{equation*}
		% Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.

		\item $u(r) \leq 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.

	\end{itemize}
\end{itemize}

@@

In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, we only need to consider the case $u(r) \leq 0$.

>>>>

The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two event that $G=\{\lambda < 0\}$, and $\overline{G} = \{\lambda > 0\}$:

	\item $\lambda < 0$
	% \begin{itemize}
		% \item $u(r) > 0$

		% % This need to be discuss further.
		% % We can have:
		% % \begin{equation*}
		% % \lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
		% % \end{equation*}
		% % Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.
		% \item $u(r) \leq 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.
	\item $\lambda > 0$
	% \begin{itemize}
	% 	% \item $u(r) > 0$

	% 	% The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.

	% 	% \item $u(r) < 0$

	% 	% This need to be discuss further.
	% 	% We can have:
	% 	% \begin{equation*}
	% 	% \lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
	% 	% \end{equation*}

	% \end{itemize}
	% \end{itemize}
\end{itemize}

@@

In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, so we only need to consider the case $u(r) \leq 0$.
